Shrinking Characteristics of Precision Matrix Estimators: An Illustration via Regression

### 2019-04-21 03-SCPME.Rmd
added libraries

# load  data
load("images/sim6.Rdata")

@@

# shrinkBO MSPE by lam and const (N = 100, P = 200, R = 10, sigma = "tridiag")
d = sigma %>% filter(N == 100, P == 200, R == 10, sparse == 0.5, sigma == "tridiag", model == "shrinkBO") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))

>>>>

# load  data
library(magrittr)
load("images/sim6.Rdata")

@@

# shrinkBO MSPE by lam and const (N = 100, P = 200, R = 10, sigma = "tridiag")
library(dplyr)
library(ggplot2)
d = sigma %>% filter(N == 100, P == 200, R == 10, sparse == 0.5, sigma == "tridiag", model == "shrinkBO") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))
